Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-15 article.qmd
Add abstract

---
title: "Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems."
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
    css: article.css
---

>>>>

---
title: "Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems."
abstract: >
    This work introduces two novel Python packages:
    Poincaré, for definition and simulation of dynamical systems,
    and SimBio, which builds on top of Poincaré to
    facilitate the definition of Chemical Reaction Networks (CRNs),
    and add support for the Systems Biology Markup Language (SBML).

    To ensure a user-friendly experience,
    they use of standard typed modern Python syntax
    that provide a seamless integration with Integrated Development Environments (IDEs),
    enhances code analysis tools, enabling error identification before execution,
    and facilitates code completion and refactoring.

    In contrast to existing Python tools for CRN modeling,
    that wrap external C/C++ libraries for simulation,
    Poincaré and SimBio are pure Python packages,
    which allows to extend their simulation capabilities by writing Python or leveraging other Python packages.
    But this does not compromise performance,
    as code can be Just-In-Time compiled with Numba,
    and benchmarks show comparable or superior performance to other tools.

    In conclusion, the Python-centric approach,
    coupled with the packages' extensibiltiy,
    positions Poincaré and SimBio as valuable tools for the modeling community.
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
    css: article.css
---
